---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# textminingR

<!-- badges: start -->
[![R-CMD-check](https://github.com/mshin77/textminingR/workflows/R-CMD-check/badge.svg)](https://github.com/mshin77/textminingR/actions)
<!-- badges: end -->

`textminingR` provides a supporting workflow for text mining analysis. The web app incorporates [quanteda](https://github.com/quanteda/quanteda) (preprocess), [stm](https://github.com/bstewart/stm) (structural topic modeling), and [ggraph](https://github.com/thomasp85/ggraph) as well as [widyr](https://github.com/dgrtwo/widyr) (network analysis). [tidytext](https://github.com/cran/tidytext) was implemented to tidy non-tidy format objects.

## Installation

You can install the released version of textminingR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("textminingR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("mshin77/textminingR")
```
## Example

Launch and browser the textminingR app:

```{r example}
library(textminingR)
# textminingR.app()
```

